---
  output:
  github_document
---

  <!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
options(digits=2)
set.seed(19861108)
```

# werner: Improve R package quality by mapping interdependence between functions.

### Installing werner

To install the latest development release of **werner**, please ensure that you are running version 3.3 or later of R and run the following code:

  ```{r, eval=F}
install.packages("devtools")
devtools::install_github("aaronrudkin/werner")
```

### Getting started

**werner** contains two main functions.

`explore_package` returns a list of connections between functions:
```{r echo=FALSE, results="hide"}
library(werner)
explore_package("werner")
```

`adjacency_matrix` returns an adjacency matrix (by default a sparse matrix from the [**Matrix**](https://cran.r-project.org/web/packages/Matrix/index.html) package, optionally a base R `matrix` object.)
```{r echo=FALSE, results="hide"}
library(werner)
adjacency_matrix("werner") # Sparse matrix
adjacency_matrix("werner", coerce_to_matrix=TRUE) # Base R matrix.
```

These adjacency matrices can be fed to [**igraph**](http://igraph.org/r/) or other graphing packages in R.
